---
title: "Daisy LMMs"
author: "Daisy & Matt"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(lme4)
library(knitr)
library(effects)
```

## Design

A 2x2x6 within participant design was employed in the experiment. 

1. The first factor relates to the ***prioritisation*** condition (no prioritisation versus prioritise position 5).
2. The second factor refers to the ***suffix*** condition (tactile suffix versus no suffix).
3. The third factor refers to the ***serial position*** (1-6). 

As in Roe et al. (2024) each participant completed 48 trials, 4 blocks of 12 tactile sequences. The tactile suffix consisted of a brush stroke across all 6 fingers, Two practice trials preceded each block. The prioritisation condition was blocked, and the order of the block was fully counterbalanced.

## Data

Read the data in from a spreadsheet.

```{r}
din=read_excel("tactile_prioritisation_suffix_longform.xlsx")
```

Knock the data into its longest form without editing any values.

```{r}
d=din %>% 
  rename(participant=PS) %>% 
  rename(block=Block) %>% 
  separate_wider_delim(Condition, names=c("priority", "suffix"), delim="/") %>% 
  mutate(suffix=tolower(suffix)) %>% 
  mutate(priority=tolower(priority)) %>% 
  mutate(suffix=str_replace(suffix, " ", "_")) %>% 
  mutate(priority=str_replace(priority, " ", "_")) %>% 
  group_by(participant) %>% 
  mutate(trial=seq_along(participant)) %>% 
  ungroup() %>% 
  mutate(trial=as_factor(trial)) %>% 
  relocate(participant, block, trial) %>% 
  pivot_longer(cols=c(Accuary_SP1, Accuary_SP2, Accuary_SP3, Accuary_SP4, Accuary_SP5, Accuary_SP6), values_to="accuracy", names_to="serial_position") %>% 
  mutate(serial_position = readr::parse_number(serial_position)) %>% 
  mutate(participant=as_factor(participant)) %>% 
  #mutate(block=as_factor(block)) %>% 
  mutate(serial_position=as_factor(serial_position)) %>% 
  mutate(priority = factor(priority, levels=c("no_priority", "p5"), labels=c("PrioritiseNone", "PrioritisePos5"))) %>% 
  mutate(suffix = factor(suffix, levels=c("no_suffix", "suffix"), labels=c("SuffAbsent", "SuffPresent"))) 
```

View the first few rows of the longest-form data.

```{r}
kable(head(d))
```

Visualise how accuracy varies across the manipulations of serial_position and priority.

```{r}
ggplot(data=d, aes(y=accuracy, x=serial_position, colour=priority))+
  facet_wrap(~suffix)+
  stat_summary(fun.data="mean_se")+
  stat_summary(fun.data="mean_se", geom='line', aes(group=priority))+
  theme_bw()+
  theme(panel.grid=element_blank())+
  #scale_x_continuous(breaks=1:6)+
  labs(title = "Accuracy improves at position 5 (but not at other positions)\n when it is prioritised versus when it is not prioritised")
```

## Modelling

Our first model will not try to capture the influence of prioritising position 5 at position 5.

```{r}
# build the actual model
m1 = glmer(
  data=d,
  family=binomial,
  formula=
        accuracy ~ block + suffix + 
          serial_position + priority + 
          (1 | participant) + 
          (1 | trial)
)

# just some visual formatting
result_m1 = coef(summary(m1)) %>% as_tibble(rownames="effect") %>% 
  rename(p=`Pr(>|z|)`) %>% 
  mutate(sig=ifelse(p<.001, "***", ifelse(p<.01, "**", ifelse(p<0.05, "*", ""))))

# show a table
kable(result_m1, digits=3)
```

In our next model, we particularly want to evaluate the interaction between serial_position and whether position 5 was prioritised or not. We see in the last row of the table that the interaction of serial position and whether we prioritise position 5 is significant.

```{r}
# build the actual model
m2 = glmer(data=d,
  family=binomial,
  formula=
        accuracy ~ block + suffix + 
          serial_position + priority + serial_position:priority +
          (1 | participant) + 
          (1 | trial)
        )

# just some visual formatting
result_m2 = coef(summary(m2)) %>% as_tibble(rownames="effect") %>% 
  rename(p=`Pr(>|z|)`) %>% 
  mutate(sig=ifelse(p<.001, "***", ifelse(p<.01, "**", ifelse(p<0.05, "*", ""))))

# show a table
kable(result_m2, digits=3)
```

Now we try to capture the 3-way interaction between suffix, serial position, and priority. ***"...addition of suffix would significantly reduce the prioritisation effect at position 5..."***

```{r}
# build the actual model
m3 = glmer(data=d,
           family=binomial,
           formula=
        accuracy ~ block + 
          suffix + serial_position + priority +
          serial_position:priority+
          suffix:serial_position:priority+
          (1 | participant) + 
          (1 | trial)
        )

# just some visual formatting
result_m3 = coef(summary(m3)) %>% as_tibble(rownames="effect") %>% 
  rename(p=`Pr(>|z|)`) %>% 
  mutate(sig=ifelse(p<.001, "***", ifelse(p<.01, "**", ifelse(p<0.05, "*", ""))))

# show a table
kable(result_m3, digits=3)
```


```{r}
d=d %>% filter(serial_position==5)
m4=glmer(data=d,
      family=binomial,
      formula=
        accuracy ~ block + suffix * priority +
        (1 + suffix + priority | participant) + 
        (1 + suffix + priority | trial)
)

# just some visual formatting
result_m4 = coef(summary(m4)) %>% as_tibble(rownames="effect") %>% 
  rename(p=`Pr(>|z|)`) %>% 
  mutate(sig=ifelse(p<.001, "***", ifelse(p<.01, "**", ifelse(p<0.05, "*", ""))))

# show a table
kable(result_m4, digits=3)

plot(allEffects(m4))

# qqplot of the random effects with their variances
lattice::qqmath(ranef(m4, condVar = TRUE), strip = FALSE)$participant

lattice::qqmath(ranef(m4, condVar = TRUE), strip = FALSE)$trial

```

